---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dualmarker

<!-- badges: start -->
<!-- badges: end -->

The goal of dualmarker is to analysis dual marker for response and survival using logistic regression and cox model

## Installation

You can install the released version of dualmarker from [github](https://github.com/) with: devtools::install("maxiaopeng/dualmarker")

```{r, include=F}
library(dualmarker)
library(stringr)
library(dplyr)
```

## dataset
We demonstrate the data using Imvigor210 result. 

## Example1
Here we demonstrated the visitation of TMB and TGFb signature for response and survival analysis

```{r example, fig.width=6, fig.height=5, include=F, warning=F, message=F}
## basic example code
res.pair <- dm_pair(data = clin_bmk_IMvigor210, response = "binaryResponse", 
        response.pos = "CR/PR", response.neg = "SD/PD", 
        marker1 = "TMB", 
        marker2 = "gepscore_TGFb.19gene")
```

plot1: single-markers
```{r, fig.width=5, fig.height=3}
res.pair$plot$single.marker
```

plot2: Scatter-chart
```{r, fig.width=4, fig.height=3}
res.pair$plot$scatter.chart
```

plot3: Four-quadrant response rate
```{r, fig.width=6, fig.height=5}
res.pair$plot$response.4quad
```

plot4: ROC curve
```{r, fig.width=5, fig.height=4}
res.pair$plot$roc
```
plot5: KMplot, not available
plot6: four-quadrant show of survival

stats-1: four quadrant statistics
```{r}
res.pair$stats$response.4quad$param
res.pair$stats$response.4quad$pos.n
res.pair$stats$response.4quad$total.n
res.pair$stats$response.4quad$stats.4quad
```

stats-2: summary of logit
```{r}
glimpse(res.pair$stats$logit)
```

stats-3:  summary of survival in each quadrant(not available here)
stats-4:  summary of cox(not available here)

## Example2
Here we demonstrated the visualization of CXCL13 expression and ARID1A mutation status
```{r fig.width=6, fig.height=5, warning=F}
res.pair <- dm_pair(data = clin_bmk_IMvigor210, 
               time = "os", event = "censOS",
               marker1 = "mut_ARID1A", marker2 = "gep_CXCL13", 
               m1.cat.pos = "YES", m1.cat.neg = "NO")
```

plot1: single markers(not available here)
plot2: scatter chart( not available here)
plot3: Four-quadrant response rate( not available here)
plot4: ROC curve( not available here)
plot5: KMplot
```{r,  fig.width=5, fig.height=5}
res.pair$plot$KMplot$marker1
res.pair$plot$KMplot$marker2
```
```{r, fig.width=5, fig.height=6}
res.pair$plot$KMplot$dualmarker
```

plot6: four-quadrant show of survival
```{r, fig.width=6, fig.height=5}
res.pair$plot$surv.4quad
```

stats-1: four quadrant response(not available)
stats-2: summary of logit for response(not available)
stats-3:  summary of survival in each quadrant
```{r}
res.pair$stats$surv.4quad$param
res.pair$stats$surv.4quad$stats
```

stats-4:  summary of cox
```{r}
glimpse(res.pair$stats$cox)
```

## Example3
find the candidate marker2 in gene signatures to combine with ARID1A mutation, using ECOG, metastatistic-status as the confounding factor
```{r}
m2.candidates <- str_subset(colnames(clin_bmk_IMvigor210),"gep_") 
res.m2.cox <- dm_searchM2_cox(
  data = clin_bmk_IMvigor210, 
   # survival
   time = "os", 
   event = "censOS",
   # marker1
   marker1 = "mut_ARID1A", 
   m1.binarize = T, 
   m1.cat.pos = "YES", 
   m1.cat.neg = "NO", 
   # marker2
   m2.candidates = m2.candidates
  )
```

Plot the searchM2 result, the top20 most significant marker2 will be shown
```{r}
plot.m2.cox <- dm_searchM2_topPlot(res.m2.cox, top.n = 30)
```

plot-1, 'm2_effect' is dot-chart, showing the top significant marker2s, whose introduction to dual-maker model(w/ or w/o interaction) significantly increase the prediction of survival. Likelihood ratio test(LRT) is carried out to compare dual-marker model and marker1 solo model, the signed log10-pValue is shown on x-axis, and 'sign' indicates the effect direction of marker2 to survival.
```{r}
plot.m2.cox$m2_effect
```

plot-2: 'interaction' is dot-chart, showing the top significant marker2s, which has statistical interaction with given marker1. Signed log10-pValue is shown like 'm2_effect'
```{r, fig.width=4, fig.height=5}
plot.m2.cox$interact
```

plot-3: 'm1_m2_effect' is scatter-plot, showing the log10-pValue of model comparison, i.e. dual-vs-marker1 and dual-vs-marker2. Dual model that superior to both marker1 and marker2 is preferred, located top-right on the figure.
```{r}
plot.m2.cox$m1_m2_effect
```

resulting table: 
```{r}
glimpse(res.m2.cox)
```

## Example 4
```{r fig.width=6, fig.height=5, warning=F}
res.pair <- dm_pair(data = clin_bmk_IMvigor210, 
               time = "os", event = "censOS",
               response = "binaryResponse", response.pos = "CR/PR", response.neg = "SD/PD",
               marker1 = "mut_ARID1A", marker2 = "gep_HMGB1", 
               m1.cat.pos = "YES", m1.cat.neg = "NO")
```

```{r, fig.height=5, fig.width=6}
res.pair$plot
```

