---
title: "intro_dualmarker"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro_dualmarker}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include=F}
library(dualmarker)
library(stringr)
library(dplyr)
```

## dataset
We demonstrate the data using Imvigor210 result. 

## Example1
Here we demonstrated the visitation of TMB and TGFb signature for response and survival analysis

```{r example, fig.width=6, fig.height=5, include=F, warning=F, message=F}
## basic example code
res.pair1 <- dm_pair(data = clin_bmk_IMvigor210, response = "binaryResponse", 
        response.pos = "CR/PR", response.neg = "SD/PD", 
        marker1 = "TMB",
        #marker2 = "mut_NCOR1", m2.cat.pos = "YES", m2.cat.neg = "NO")
        marker2 = "TC.Level", m2.cat.pos = "TC0", m2.cat.neg = c("TC1","TC2+"))
        #marker2 = "gepscore_TGFb.19gene")
```

plot1: single-markers
```{r, fig.width=5, fig.height=3}
res.pair1$plot$single.marker
```

plot2: Scatter-chart
```{r, fig.width=4, fig.height=3}
res.pair1$plot$scatter.chart
```

plot3: Four-quadrant response rate
```{r, fig.width=6, fig.height=5}
res.pair1$plot$response.4quad
```

plot4: ROC curve
```{r, fig.width=5, fig.height=4}
res.pair1$plot$roc
```
plot5: KMplot, not available
plot6: four-quadrant show of survival

stats-1: four quadrant statistics
```{r}
res.pair1$stats$response.4quad$param
res.pair1$stats$response.4quad$pos.n
res.pair1$stats$response.4quad$total.n
res.pair1$stats$response.4quad$stats.4quad
```

stats-2: summary of logit
```{r}
glimpse(res.pair$stats$logit)
```

stats-3:  summary of survival in each quadrant(not available here)
stats-4:  summary of cox(not available here)

## Example2
Here we demonstrated the visualization of CXCL13 expression and ARID1A mutation status
```{r fig.width=6, fig.height=5, warning=F}
res.pair2 <- dm_pair(data = clin_bmk_IMvigor210, 
               time = "os", event = "censOS",
               marker1 = "mut_ARID1A", marker2 = "gep_CXCL13", 
               m1.cat.pos = "YES", m1.cat.neg = "NO")
```

plot1: single markers(not available here)
plot2: scatter chart( not available here)
plot3: Four-quadrant response rate( not available here)
plot4: ROC curve( not available here)
plot5: KMplot
```{r,  fig.width=5, fig.height=5}
res.pair2$plot$KMplot$marker1
res.pair2$plot$KMplot$marker2
```
```{r, fig.width=5, fig.height=6}
res.pair2$plot$KMplot$dualmarker
```

plot6: four-quadrant show of survival
```{r, fig.width=6, fig.height=5}
res.pair2$plot$surv.4quad
```

stats-1: four quadrant response(not available)
stats-2: summary of logit for response(not available)
stats-3:  summary of survival in each quadrant
```{r}
res.pair$stats$surv.4quad$param
res.pair$stats$surv.4quad$stats
```

stats-4:  summary of cox
```{r}
glimpse(res.pair$stats$cox)
```



## Example2.2
Here we demonstrated the visualization of CXCL13 expression and ARID1A mutation status
```{r fig.width=6, fig.height=5, warning=F}
res.pair2 <- dm_pair(
   data = clin_bmk_IMvigor210, 
   response = "binaryResponse", 
   response.pos = "CR/PR", response.neg = "SD/PD",
   time = "os", event = "censOS",
   marker1 = "IC.Level", marker2 = "mut_FGF10", 
   m1.cat.pos = c("IC1","IC2+"), m1.cat.neg = "IC0",
   m2.cat.pos = "YES", m2.cat.neg = "NO")
```

```{r}
res.pair2$plot
```



## Example3
Here we demonstrated searchM2 function to combine with TMB for signatures
```{r}
m2.candidates <- str_subset(colnames(clin_bmk_IMvigor210),"gepscore_")
length(m2.candidates)
res.m2.logit <- dm_searchM2_logit(
   data = clin_bmk_IMvigor210, 
    # response info
    response = "binaryResponse", 
    response.pos = "CR/PR", 
    response.neg = "SD/PD", 
    # marker1
    marker1 = "TMB",
    m1.binarize = F, # use continuous variables
    # marker2
    m2.candidates = m2.candidates, 
   # coufounding factor
   # confound.factor = c("Baseline.ECOG.Score","Met.Disease.Status")
   confound.factor = "Immune.phenotype"
   )
```

Plot searchM2 result
```{r}
plot.m2.logit <- dm_searchM2_topPlot(res.m2.logit)
```

plot-1: m2 effect
```{r}
plot.m2.logit$m2_effect
```
plot-2: interaction
```{r}
plot.m2.logit$interact
```
plot-3: scatterplot of dualmarker vs. m1 and dualmarker vs m2
```{r, fig.width=7, fig.height=7}
plot.m2.logit$m1_m2_effect
```

stats
```{r}
dplyr::glimpse(res.m2.logit)
```

## Example4
Here we demonstrated searchM2 function to combine with TMB for signatures
```{r}
m2.candidates <- str_subset(colnames(clin_bmk_IMvigor210),"mut_")
length(m2.candidates)
res.m2.logit <- dm_searchM2_logit(
   data = clin_bmk_IMvigor210, 
    # response info
   response = "binaryResponse", 
   response.pos = "CR/PR", 
   response.neg = "SD/PD", 
    # marker1
   marker1 = "TMB",
   m1.binarize = F, # use continuous variables
    # marker2
   m2.candidates = m2.candidates, 
   m2.binarize = T, 
   m2.cat.pos = "YES", m2.cat.neg = "NO",
   # coufounding factor
   # confound.factor = c("Baseline.ECOG.Score","Met.Disease.Status")
   confound.factor = "Immune.phenotype"
   )
```
```{r}
dm_searchM2_topPlot(res.m2.logit)

```


## Example5
find the candidate marker2 in gene signatures to combine with ARID1A mutation, using ECOG, metastatistic-status as the confounding factor
```{r}
m2.candidates <- str_subset(colnames(clin_bmk_IMvigor210),"gep_") 
res.m2.cox <- dm_searchM2_cox(
  data = clin_bmk_IMvigor210, 
   # survival
   time = "os", 
   event = "censOS",
   # marker1
   marker1 = "mut_ARID1A", 
   m1.binarize = T, 
   m1.cat.pos = "YES", 
   m1.cat.neg = "NO", 
   # marker2
   m2.candidates = m2.candidates
   # confounding factor
   #confound.factor = c("Baseline.ECOG.Score","Met.Disease.Status")
  #confound.factor = "Immune.phenotype"
  )
```

Plot the searchM2 result, the top20 most significant marker2 will be shown
```{r}
plot.m2.cox <- dm_searchM2_topPlot(res.m2.cox, top.n = 30)
```

plot-1, 'm2_effect' is dot-chart, showing the top significant marker2s, whose introduction to dual-maker model(w/ or w/o interaction) significantly increase the prediction of survival. Likelihood ratio test(LRT) is carried out to compare dual-marker model and marker1 solo model, the signed log10-pValue is shown on x-axis, and 'sign' indicates the effect direction of marker2 to survival.
```{r}
plot.m2.cox$m2_effect
```

plot-2: 'interaction' is dot-chart, showing the top significant marker2s, which has statistical interaction with given marker1. Signed log10-pValue is shown like 'm2_effect'
```{r, fig.width=4, fig.height=5}
plot.m2.cox$interact
```

plot-3: 'm1_m2_effect' is scatter-plot, showing the log10-pValue of model comparison, i.e. dual-vs-marker1 and dual-vs-marker2. Dual model that superior to both marker1 and marker2 is preferred, located top-right on the figure.
```{r}
plot.m2.cox$m1_m2_effect
```

resulting table: 
```{r}
glimpse(res.m2.cox)
```

# Example 6
```{r}
m2.candidates <- str_subset(colnames(clin_bmk_IMvigor210),"mut_") %>% setdiff(., "mut_ARID1A")
length(m2.candidates)
res.m2.cox <- dm_searchM2_cox(
   data = clin_bmk_IMvigor210, 
    # survival info
   time = "os", 
   event = "censOS", 
    # marker1
   marker1 = "mut_ARID1A",
   m1.binarize = T, # use continuous variables
   m1.cat.pos = "YES", m1.cat.neg = "NO",
    # marker2
   m2.candidates = m2.candidates, 
   m2.binarize = T, 
   m2.cat.pos = "YES", m2.cat.neg = "NO"
   # coufounding factor
   # confound.factor = c("Baseline.ECOG.Score","Met.Disease.Status")
   # confound.factor = "Immune.phenotype"
   )
```

```{r}
dm_searchM2_topPlot(res.m2.cox)
```

# Example 7
```{r}
m2.candidates <- str_subset(colnames(clin_bmk_IMvigor210),"mut_")
length(m2.candidates)
res.m2.logit <- dm_searchM2_logit(
   data = clin_bmk_IMvigor210, 
   # survival info
   response = "binaryResponse", 
   response.pos = "CR/PR", response.neg = "SD/PD", 
   # marker1
   marker1 = "IC.Level",
   m1.binarize = T,
   m1.cat.neg = "IC0", m1.cat.pos = c("IC1","IC2+"),
    # marker2
   m2.candidates = m2.candidates, 
   m2.binarize = T,
   m2.cat.pos = "YES", m2.cat.neg = "NO"
   # coufounding factor
   # confound.factor = c("Baseline.ECOG.Score","Met.Disease.Status")
   # confound.factor = "Immune.phenotype"
   )
```


```{r}
dm_searchM2_topPlot(res.m2.logit, top.n = 20)
```

# Example 8
```{r}
m2.candidates <- str_subset(colnames(clin_bmk_IMvigor210),"mut_")
length(m2.candidates)
res.m2.cox <- dm_searchM2_cox(
   data = clin_bmk_IMvigor210, 
   # survival info
   time = "os", 
   event = "censOS",
   # marker1
   marker1 = "IC.Level",
   m1.binarize = T,
   m1.cat.neg = "IC0", m1.cat.pos = c("IC1","IC2+"),
    # marker2
   m2.candidates = m2.candidates, 
   m2.binarize = T,
   m2.cat.pos = "YES", m2.cat.neg = "NO"
   # coufounding factor
   # confound.factor = c("Baseline.ECOG.Score","Met.Disease.Status")
   # confound.factor = "Immune.phenotype"
   )
```

```{r}
dm_searchM2_topPlot(res.m2.cox)
```
# example 10
```{r}
candidates <- str_subset(colnames(clin_bmk_IMvigor210),"gepscore_")
res.sm.logit <- sm_searchM_logit(data = clin_bmk_IMvigor210, 
                 response = "binaryResponse", 
                 response.pos = "CR/PR", response.neg = "SD/PD", 
                 candidates = candidates, binarize = F)
sm_searchM_topPlot(res.sm.logit)
```
# example 11
```{r}
candidates <- str_subset(colnames(clin_bmk_IMvigor210),"mut_")
res.sm.logit <- sm_searchM_logit(data = clin_bmk_IMvigor210, 
                 response = "binaryResponse", 
                 response.pos = "CR/PR", response.neg = "SD/PD", 
                 candidates = candidates, binarize = T, 
                 cat.pos = "YES", cat.neg = "NO")
sm_searchM_topPlot(res.sm.logit)
```

# example 12
```{r}
candidates <- str_subset(colnames(clin_bmk_IMvigor210),"gepscore_")
res.sm.cox <- sm_searchM_cox(data = clin_bmk_IMvigor210, 
                 time = "os", event= "censOS", 
                 candidates = candidates, binarize = F)
sm_searchM_topPlot(res.sm.cox)
```

```{r}
candidates <- str_subset(colnames(clin_bmk_IMvigor210),"mut_")
res.sm.cox <- sm_searchM_cox(data = clin_bmk_IMvigor210, 
                 time = "os", event= "censOS", 
                 candidates = candidates, binarize = T,
                 cat.pos = "YES", cat.neg = "NO")
sm_searchM_topPlot(res.sm.cox)
```
